Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-04-18 Masterarbeit_Robotik_Pamuk.tex
add papers

\noindent Without CPU isolation, context switches take place at operating system level and not at hypervisor level. This explains why there are fewer \texttt{kvm\_exit} events. However, this will also, as previously shown, lead to higher latency, as context switches at operating system level generally take longer than a \texttt{kvm\_exit} and kvm\_entry.

\noindent When the CPU was dedicated to the QEMU process, on the other hand,there was a significant increase in \texttt{kvm\_exit} events. This is because every context switch takes place at hypervisor level. Nevertheless, lower latency was achieved thereby, as the qemu process is no longer influenced by the CPU scheduling of the operating system.

>>>>

\noindent In the following, the host and guest tasks along with their impact on system latency are briefly described.

\begin{itemize} 
	\item \textbf{qemu-system-x86}: Part of the QEMU process and specifically, this task emulates x86 systems. In table \ref{tab:results_host_report}, it occurs four times under different PIDs, hence there are four threads of it.
	\item \textbf{<idle>}: This represents the idle time of the CPU, hence it is not being used by any process. 
	\item \textbf{vhost}: A kernel module which improves virtio (virtual input/output) performance by handling virtqueues in the kernel, thereby reducing context switches and system calls. 
	\item \textbf{kworker/19:1}: A kernel worker thread created by the Linux kernel, kworker/19:1 performs work in response to system events. The number after the slash and colon indicate the CPU core and internal ID of the worker thread, respectively. 
	\item \textbf{kworker/19:1H}: Similar to kworker/19:1, kworker/19:1H is a kernel worker thread, with the ‘H’ suggesting that this thread handles hardware interrupts. 
	\item \textbf{migration/19}: The migration process is a kernel process that balances load across CPU cores by moving threads from one CPU to another. The number after the slash indicates the CPU core to which the migration process is bound. 
\end{itemize}

 qemu-system-x86 
 <idle> 
 vhost 
 qemu-system-x86 
 qemu-system-x86 
 qemu-system-x86 
 kworker/19:1 
 kworker/19:1H 
 migration/19

\begin{comment}
\noindent Without CPU isolation, context switches take place at operating system level and not at hypervisor level. This explains why there are fewer \texttt{kvm\_exit} events. However, this will also, as previously shown, lead to higher latency, as context switches at operating system level generally take longer than a \texttt{kvm\_exit} and kvm\_entry.

\noindent When the CPU was dedicated to the QEMU process, on the other hand,there was a significant increase in \texttt{kvm\_exit} events. This is because every context switch takes place at hypervisor level. Nevertheless, lower latency was achieved thereby, as the qemu process is no longer influenced by the CPU scheduling of the operating system.
\end{comment}
